\centering DAOSYS: Smart DAO Protocol for Decentralized Finance

### 2022-09-22 latex/whitepaper/article.tex
whitepaper draft

\begin{itemize}
  \item Smart DAO protocol via hyper-diamond proxy
  \item Self-sovereign via trustless automatic integration
  \item Seamless fast deployment using secure templates
  \item Hyper-diamond standard
  \item Collateralized VE (vesting) indexing token
  \item Automated audits of child DAOs
  \item Fully backed (eg, DAI, SYS)
  \item Non-spectualtive asset
  \item New emergent behavior and innovation for DeFi
\end{itemize}

@@

DOAs are governance structures for groups of people to come together and make decisions, which is one of its main distinguishing features. Unlike traditional organizations (e.g., private companies, non-governmental organizations, charities, etc.) which have a centralized structure, these decisions are coordinated and enforced on a blockchain in a decentralized manner. Since DAOSYS proposes to be autonomous and fully decentralized, it has no top level governance.

@@

The tokenomics model representing the minimum commitment of verified child DOAs is illustrated in five steps in Fig. \ref{fig:tokenomics_model}. This model represents a symbiotic relationship between DAOSYS and its respective child DOAs. This is where verified child DAOs receives the interest generated from its own collateral and DAOSYS receives debt-based interest generated from that collateral.

Included in this symbiotic relationship are several other benefits that child DOAs will have by joining this network over building its own standalone DAO. New DAOs benefit from significantly fast development time by selecting any one of the pre-vetted, secure DAOSYS templates. Included in this, DAOs can simulate the tokenomic behavior prior to launch using our Python simulator tailored to our system (as detailed in next Section) to build predictive models to determine 2-5 year estimated ROI calculations. DAOs that are part of our network will also benefit from the seamless integrations of working with other DAOs within our network. These integrations would be akin to the benefits nation states have when they join international trade agreements, where DAOSYS behaves as the overseeing regulatory body, and the child DAOs share attributes as participating nation states. These child DAOs also have the flexibility of cloning the DAOSYS factory and spawning its own sub-network within the DAOSYS ecosystem; see Fig. \ref{fig:clone_model}.

@@

It is surprising that with all the developments that have happened in crypto, and given the success that ETFs have had in traditional finance we have not yet seen adoption of this idea into crypto yet. However, DAOSYS with its smart DOA features will allow for the secure and seamless deployment of these new class of cryptos.

@@

In this discussion we present the first ever smart DAO protocol; this idea is similar to Ethereum in the sense that both protocols work with decentralized immutable storage. However, instead launching contracts from chains, we work with Diamonds by exploiting the multi-facet proxy that was first presented in EIP-2535 \cite{Mud20}.

>>>>

\begin{itemize}
  \item Smart DAO protocol via hyper-diamond proxy
  \item Self-sovereign via trustless automatic integration
  \item Seamless fast deployment using secure templates
  \item Hyper-diamond standard
  \item Collateralized VE (vesting) indexing token
  \item Automated audits of child DAOs
  \item Fully backed (eg, DAI, SYS)
  \item Non-spectualtive asset
  \item No code or low code deploymments via user interface
  \item New emergent behavior and innovation for DeFi
\end{itemize}

@@

DAOs are governance structures for groups of people to come together and make decisions, which is one of its main distinguishing features. Unlike traditional organizations (e.g., private companies, non-governmental organizations, charities, etc.) which have a centralized structure, these decisions are coordinated and enforced on a blockchain in a decentralized manner. Since DAOSYS proposes to be autonomous and fully decentralized, it has no top level governance.

@@

The tokenomics model representing the minimum commitment of verified child DAOs is illustrated in five steps in Fig. \ref{fig:tokenomics_model}. This model represents a symbiotic relationship between DAOSYS and its respective child DAOs. This is where verified child DAOs receives the interest generated from its own collateral and DAOSYS receives debt-based interest generated from that collateral.

Included in this symbiotic relationship are several other benefits that child DAOs will have by joining this network over building its own standalone DAO. New DAOs benefit from significantly fast development time by selecting any one of the pre-vetted, secure DAOSYS templates. Included in this, DAOs can simulate the tokenomic behavior prior to launch using our Python simulator tailored to our system (as detailed in next Section) to build predictive models to determine 2-5 year estimated ROI calculations. DAOs that are part of our network will also benefit from the seamless integrations of working with other DAOs within our network. These integrations would be akin to the benefits nation states have when they join international trade agreements, where DAOSYS behaves as the overseeing regulatory body, and the child DAOs share attributes as participating nation states. These child DAOs also have the flexibility of cloning the DAOSYS factory and spawning its own sub-network within the DAOSYS ecosystem; see Fig. \ref{fig:clone_model}.

@@

It is surprising that with all the developments that have happened in crypto, and given the success that ETFs have had in traditional finance we have not yet seen adoption of this idea into crypto yet. However, DAOSYS with its smart DAO features will allow for the secure and seamless deployment of these new class of cryptos.

@@

In this discussion we present the first ever smart DAO protocol; this idea is similar to Ethereum in the sense that both protocols work with decentralized immutable storage. However, instead launching contracts from chains, we work with Diamonds by exploiting the multi-facet proxy that was first presented in EIP-2535 \cite{Mud20}. To make the analogy, if Ethereum is the UNIX platform, then DAOSYS is the enterprise development system, which is utilized via low code or no code deployments.
